Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
contributions

\item We exploit a CEGIS-based approach, that uses inductive synthesis
in conjunction with a formal verification algorithm, for synthesising 
correct-by-design robust digital controllers for non-fragile closed-loop 
stability.

\item Experiments obtained with our synthesiser show that the combination 
of interval arithmetic to represent the controller coefficients and a two-stage 
verification approach to continuously refine precision, we are able to compute 
a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
given a set of continuous and discrete plant with parametric uncertainties.

\end{itemize}

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with an algorithm for verifying robust closed-loop stability, 
in order to compute a parametric solution for a digital controller given 
a continuous (or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.

>>>>

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is not trivial 
and requires addressing challenges specific to
control systems such as handling the effects of quantisers 
and FWL.

\item We provide experimental results showing that
our fully automatic CEGIS-based approach is able to synthesise 
stable controllers for a set of intricate benchmarks taken from 
the literature in a reasonable amount of time 
(the median runtime for our benchmark set is 197s, 
implying that half of the controllers can be synthesised in less
than 5 minutes). 
\end{itemize}

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with a robust algorithm for verifying closed-loop stability to
compute a parametric solution for a digital controller given a continuous
(or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.
